Method Reuse for a Deep Web Question Answering System

### 2010-03-05 trunk/paper/semsearch10/content/example.tex
final update before ....

The end-user employs the Morpheus question-answering system much like a
search engine with a natural-language interface. One can type a question
in a text box and receive a response from the system. Those questions
dealing with an ontological realm familiar to the system, whose form is
similar to previously answered queries in that realm, and that can be
answered using (possibly deep web) information from a source the system
has encountered can yield relevant responses.

\begin{figure}
\caption{Typical Morpheus interaction}
\label{fig:screenshot}
\end{figure}

Figure \ref{fig:screenshot} shows a screenshot of a typical Morpheus
interaction. The user has typed a question ``Blah blah blah!!!!!!?'' and
received a response together with information describing assumptions
about the question, the likely relevance of the answer provided,
the source of information, and the method of answer production.

Each answer to a question is created using a {\it query response
  method} (QRM). A QRM is constructed when a special user, known as a
{\it guide} answers a question using an instrumented web browser (the
{\it query response recorder} or QRR) that records web
interactions. The system extracts the relevant artifacts of the
guide's actions and stores them in the QRM. The QRM is characterized
by a {\it semi-structured query} (SSQ), a schematic representation of
the information contained in the query, namely the inputs and output
contexts---the {\it who, what, when,} and {\it where}
categories---that characterize the question together with an
appropriately generalized representation of the guide's browser
interactions.  The {\it query response evaluator} (QRE) evaluates a
query by binding specific arguments to its input parameters and
replaying the generalized web interactions the guide used to answer
the original question.

To answer a user's question, we must identify likely contextual
categories associated with the terms in the question to form an SSQ,
find those QRMs having contextually compatible SSQs, then use the QRE to
generate a response.

In what follows, we detail the elements of the system.  We first
discuss the processing of natural language queries to generate SSQs.
Next, we discuss the recording of guide behavior with the QRR.  We
then discuss how the categorical heterarchies associated with
ontological realms are constructed in a semi-automated fashion.  We
describe the method we use to assess how well a stored QRM matches a
user SSQ.  We then discuss the QRM evaluation process and discuss the
system's behavior on example queries. We conclude with a discussion of
future work.

>>>>

%jnw

The end-user employs the Morpheus question-answering system much like a search engine with a natural-language interface. One can type a question in a text box and receive a response from the system. The system uses previously answered queries to answer new questions.  The reused questions have a similar form and the same ontological realm, and employ sources that will yield relevant solutions.  We focus our reuse on the sources that are hidden behind web forms, or the \emph{deep web}.

Suppose the user poses the question ``A 1997 Toyota Camry V6 needs what size tires?'' The answer (205-65-15) will be presented, together with information describing assumptions about the question, the likely relevance of the answer provided,
the source of information, and the method of answer production.

Each answer to a question is created using a \emph{query response
  method} (QRM). A QRM is constructed when a special user, known as a
\emph{guide}, answers a question using an instrumented web browser (the
\emph{query response recorder} or QRR) that records web
interactions. The system extracts the relevant artifacts of the
guide's actions and stores them in the QRM. The QRM is characterized
by a \emph{semi-structured query} (SSQ), a schematic representation of
the information contained in the natural language question, namely the input and output
contexts---the \emph{who, what, when,} and \emph{where}
categories---that characterize the question.  In addition, the QRR has categorized a generalized representation of the guide's browser
interactions.  The \emph{query response evaluator} (QRE) evaluates a
query by binding specific arguments to its input parameters and
replaying the generalized web interactions the guide used to answer
the original question.

To answer a user's question, we must identify likely contextual
categories associated with the terms in the question to form an SSQ,
find those QRMs having contextually compatible SSQs, and then use the QRE to
generate a response.

In what follows, we detail the elements of the system.  We first
discuss how the processing of natural language queries generates SSQs.
Next, we discuss the recording of guide behavior with the QRR.  We
then discuss how the categorical heterarchies associated with
ontological realms are constructed in a semi-automated fashion.  We
describe the method we use to assess how well a stored QRM matches a
user SSQ.  We then discuss the QRM evaluation process and the
system's behavior for example queries. We conclude with a discussion of
future work.

### 2010-03-05 trunk/paper/semsearch10/content/results_futurework_conclusion.tex
final update before ....

Because each QRM may be treated as a function, we plan on leveraging
previous work to allow new questions to be solved by connecting
together several QRMs \cite{morpheus1, transformscout}.  This method
would expand the types of queries that are answerable by the system.

Currently, the category heterarchy generated from the DBpedia
categories and our SSQ ontologies is stored in separate XML files. We
are in the process of moving these ontologies into an efficient
ontology database. Similarly, employing user input brings about the
likelihood that redundant SSQ ontological elements will be inserted
into our ontology store. We are working on merging the similar SSQs
[\ref{sec:ssq}] based on the SSQ realms and other ontological
structural information so that we can remove the redundancy in the
database.

We cannot rely on the DBpedia categories and the associated Wikipedia
pages to provide corpora for all our realms.  The DBpedia categories
and the associated Wikipedia documents are insufficient to
characterize the linguistic space of queries belonging to many
different realms.  Reasonable prior probabilities for the names of
musical groups within the category \emph{musical groups}, for example,
will be significantly different from what would be manufactured by
simply finding n-gram frequency within the related Wikipedia
documents. We are investigating methods to identify categories within
the deep web and to find new sources to construct \textit{weak} realms
in our ontology hierarchy.

%% I may have misstated the statistics that are unique/repeats
% need to clarify the statistics 
%% Add language about how we 
Researchers have stated that somewhere from 39 to 63 percent of web
queries are unique \cite{1277770,331405,621942}.  We believe that a
large percentage of the stated unique queries are in-fact related and
parameterizable, meaning, several subsets of unique queries may be all
related and may be answered using a single QRM.  It is difficult to
discover this property between queries.  Previous work suggest
techniques to find related queries but it will take new efficient
methods to discover parameterizable queries.

@@

In this paper we provide a discussion on a new type of question
answering system that uses previously answered user questions.  We
described our method of modeling a users question answering process
and how we are able to discover semantically similar queries.

\section{Acknowledgements}

>>>>

Because each QRM may be treated as a function, we plan to use
previous work to allow new questions to be solved by connecting
together several QRMs \cite{morpheus1, transformscout}.  This method
would expand the types of queries that are answerable by the system.

Employing user input brings about the
likelihood that redundant SSQ ontological elements will be inserted
into our ontology store. We are working on merging the similar SSQs
[\ref{sec:ssq}] based on the SSQ realms and other ontological
structural information so that we can remove the redundancy in the
database.  Currently, the category heterarchy generated from the DBpedia
categories and our SSQ ontologies is stored in separate XML files. We
are in the process of moving these ontologies into an efficient
ontology database.

The DBpedia categories
and the associated Wikipedia documents are insufficient to
characterize the linguistic space of queries belonging to many
different realms.  Reasonable prior probabilities for the names of
musical groups within the category \emph{musical groups}, for example,
will be significantly different from what would be manufactured by
simply finding n-gram frequency within the related Wikipedia
documents.

@@

In this paper we provide a discussion on a new type of question
answering system that uses previously answered user questions.  We
described our method of modeling a user's question answering process
and how we are able to discover semantically similar queries.  The Morpheus system provides many opportunities for optimization.  However, we believe this new technique for question answering system will improve the exploration experience.

\section{Acknowledgments}
Our thanks to Guillermo Cordero, and Nick Antonelli for their assistance building this system. Additionally, we would like to thank NSF for their generous support of our project.
